The Host Galaxies of Rapidly Evolving Transients in the Dark Energy Survey

### 2020-03-19 RET_Hosts_IR.tex
Updates from Overleaf

\begin{figure*}
\includegraphics[width=\textwidth]{mc_figs/rets_s12}
\caption{Histograms showing the differences between the fit parameters across the MCMC samples.
\label{fig:param_diffs}}
\end{figure*}

\begin{figure*}
\includegraphics[width=\textwidth]{mc_figs/rets_s12_ssfr_corner_final.png}
\caption{Corner plot showing the posterior samples from the MCMC fit to the DES RETs and \citet{Sanders2012} sSFRs. Notable features are: 1) the RET distribution is better constrained than the SESNe (S12); 2) the skewness (alpha) for S12 is not well constrained due do the sharp cut off at $-9.5$ (see Fig. \ref{fig:histfit_s12_ssfr}); 3) the RETs scale vs alpha distribution is two-tailed due to alpha being centered close to 0; 4) there is a degeneracy to (3) between RETs loc and alpha for the same reason.
\label{fig:corner}}
\end{figure*}

\replychris{To compare two distributions we follow the method outlined in \citet{Wiseman2020}. We fit the PDFs, along with the uncertainty on the value in each bin, simultaneously with the same priors using the No U-Turn Sampler (NUTS; \citealt{Hoffman2014}) Hamiltonian Monte Carlo algorithm via the  \texttt{pymc3}\footnote{https://docs.pymc.io/} package to explore the posterior distribution. We use a warm-up period of $5\times10^3$ iterations and a fit period of $10^4$ iterations. Fig. \ref{histfit} displays an example of the resulting fit where the DES RETs and \citet{Sanders2012} sSFR distributions are compared. Each resulting distribution is described by the `loc' (location), `scale' (spread), and `alpha' (skewness). We then compare the differences in these parameters, as seen in Fig. \ref{fig:param_diffs}, by reporting objectively the percentages of posterior samples that overlap, and subjectively what this means for the similarity of the distributions.} 
\begin{figure*}
\includegraphics[width=0.5\textwidth]{mc_figs/rets_s13_histfit_ssfr_final.png}
\caption{Results of the MCMC fits to the PDFs of sSFR for DES RETs and SNe II, accounting for uncertainties in each bin.
\label{fig:histfit}}
\end{figure*}
\begin{figure*}
\includegraphics[width=0.5\textwidth]{mc_figs/rets_k15_histfit_ssfr_final.png}
\caption{Results of the MCMC fits to the PDFs of sSFR for DES RETs and LGRBs, accounting for uncertainties in each bin.
\label{fig:histfit}}
\end{figure*}
\begin{figure*}
\includegraphics[width=0.5\textwidth]{mc_figs/rets_p16_histfit_ssfr_final.png}
\caption{Results of the MCMC fits to the PDFs of sSFR for DES RETs and SLSNe, accounting for uncertainties in each bin.
\label{fig:histfit}}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width=0.5\textwidth]{mc_figs/rets_s12_histfit_OH_final.png}
\caption{Results of the MCMC fits to the PDFs of metallicity for DES RETs and SESNe, accounting for uncertainties in each bin.
\label{fig:histfit}}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.5\textwidth]{mc_figs/rets_s13_histfit_OH_final.png}
\caption{Results of the MCMC fits to the PDFs of metallicity for DES RETs and SNe II, accounting for uncertainties in each bin.
\label{fig:histfit}}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.5\textwidth]{mc_figs/rets_k15_histfit_OH_final.png}
\caption{Results of the MCMC fits to the PDFs of metallicity for DES RETs and LGRBs, accounting for uncertainties in each bin.
\label{fig:histfit}}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.5\textwidth]{mc_figs/rets_p16_histfit_OH_final.png}
\caption{Results of the MCMC fits to the PDFs of metallicity for DES RETs and SLSNe, accounting for uncertainties in each bin.
\label{fig:histfit}}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\begin{figure*}
\includegraphics[width=\textwidth]{mc_figs/rets_s12_param_diffs_ssfr_final.png}
\caption{Histograms showing the differences between the fit parameters across the MCMC samples.
\label{fig:param_diffs}}
\end{figure*}

\begin{figure*}
\includegraphics[width=\textwidth]{mc_figs/rets_s12_ssfr_corner_final.png}
\caption{\replychris{Corner plot showing the posterior samples from the MCMC fit to the DES RETs and \citet{Sanders2012} sSFRs. Notable features are: 1) the RET distribution is better constrained than the SESNe (S12); 2) the skewness (alpha) for S12 is not well constrained due do the sharp cut off at $-9.5$ (see Fig. \ref{fig:histfit_s12_ssfr}); 3) the RETs scale vs alpha distribution is two-tailed due to alpha being centered close to 0; 4) there is a degeneracy to (3) between RETs loc and alpha for the same reason. Figure produced using the \texttt{corner} package \citep{Foreman-Mackey2016}.}
\label{fig:corner}}
\end{figure*}

\replychris{To compare two distributions we follow the method outlined in \citet{Wiseman2020}. We fit the PDFs, along with the uncertainty on the value in each bin, simultaneously with the same priors using the No U-Turn Sampler (NUTS; \citealt{Hoffman2014}) Hamiltonian Monte Carlo algorithm via the  \texttt{pymc3}\footnote{https://docs.pymc.io/} package to explore the posterior distribution. We use a warm-up period of $5\times10^3$ iterations and a fit period of $10^4$ iterations. Fig. \ref{fig:histfit} displays an example of the resulting fit where the DES RETs and \citet{Sanders2012} sSFR distributions are compared. Each resulting distribution is described by the `loc' (location), `scale' (spread), and `alpha' (skewness). We then compare the differences in these parameters, as seen in Fig. \ref{fig:param_diffs}, by reporting objectively the percentages of posterior samples that overlap, and subjectively what this means for the similarity of the distributions.} 
\twocolumn
\begin{figure}
\includegraphics[width=0.5\textwidth]{mc_figs/rets_s13_histfit_ssfr_final.png}
\caption{Results of the MCMC fits to the PDFs of sSFR for DES RETs and SNe II, accounting for uncertainties in each bin.
\label{fig:histfit}}
\end{figure}
\begin{figure}
\includegraphics[width=0.5\textwidth]{mc_figs/rets_k15_histfit_ssfr_final.png}
\caption{Results of the MCMC fits to the PDFs of sSFR for DES RETs and LGRBs, accounting for uncertainties in each bin.
\label{fig:histfit}}
\end{figure}
\begin{figure}
\includegraphics[width=0.5\textwidth]{mc_figs/rets_p16_histfit_ssfr_final.png}
\caption{Results of the MCMC fits to the PDFs of sSFR for DES RETs and SLSNe, accounting for uncertainties in each bin.
\label{fig:histfit}}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{mc_figs/rets_s12_OH_histfit_final.png}
\caption{Results of the MCMC fits to the PDFs of metallicity for DES RETs and SESNe, accounting for uncertainties in each bin.
\label{fig:histfit}}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{mc_figs/rets_s13_OH_histfit_final.png}
\caption{Results of the MCMC fits to the PDFs of metallicity for DES RETs and SNe II, accounting for uncertainties in each bin.
\label{fig:histfit}}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{mc_figs/rets_k15_OH_histfit_final.png}
\caption{Results of the MCMC fits to the PDFs of metallicity for DES RETs and LGRBs, accounting for uncertainties in each bin.
\label{fig:histfit}}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{mc_figs/rets_p16_OH_histfit_final.png}
\caption{Results of the MCMC fits to the PDFs of metallicity for DES RETs and SLSNe, accounting for uncertainties in each bin.
\label{fig:histfit}}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
